### 2017-11-21 manuscript.rmd
made supplemental phylogenetic signal table into xtable

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, echo=F, message=F, warning=F}
binaries_phylosig # make it xtable
```

>>>>

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
print(xtable_PS, scalebox=0.7)
```
